State of the Practice for Lattice Boltzmann Method Software

### 2022-04-23 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
reviewed Section 10

In this section we provide recommendations to address the pain points from
Section~\ref{painpoints} to answer~\rqref{RQ_Recommend}.  Our recommendations
are not lists of criticisms for what should have been done in the past, or what
should be done now; they are just suggestions for consideration in the future.
We will not be repeating ideas here that have been discussed in previous
sections, such as CI, documentation of APIs, etc.  Our aim
is to mention ideas that are at least somewhat beyond conventional best
practices. The ideas listed here have the potential to become best practices in
the medium to long-term. The ideas are presented roughly in the order of
increasing novelty.

@@

Except for \citet{ThielEtAl2020}, the research software guidelines that we
consulted do not mention linters.  However, we feel linters have the potential
to improve code quality at a relatively low cost.  A linter is a tool that
statically analyzes code to find programming errors, stylistic inconsistencies
and suspicious constructs \citep{Wikipedia2022_Lint}. Linters can be used to
spot check code files, or even better as part of a continuous integration
system, as discussed in Section~\ref{Sec_CompareTools}.

@@

To address the pain point of a lack of funding (\ppref{P_LackFunding}), LBM
developers should watch for new opportunities to publish their research software
source code. For instance, the Journal of Open Source Software (JOSS) reviews
and publishes articles that credit the scholarship contained in the software
itself \citep{SmithEtAl2018-joss}.  \citep{SmithEtAl2016-softcite} presents a
set of software citation principles that may encourage broad adoption of a
consistent policy for software citation across disciplines and venues.
\citep{ChueHongEtAl2019} provides a software citation checklist for developers
to make a release of their software citable.  Further guidance on software
citation is provided by \citet{KatzEtAl2021}.  Another option is to use GitHub
for citation, since it is relatively easy to add metadata to repositories and to
generate citations for those repositories \citet{Smith2021-CitationsOnGitHub}.

>>>>

In this section we provide recommendations to address the pain points from
Section~\ref{painpoints} to answer~\rqref{RQ_Recommend}.  Our recommendations
are not lists of criticisms for what should have been done in the past, or what
should be done now; they are suggestions for consideration in the future.
We will not be repeating ideas here that have been discussed in previous
sections, such as CI, documentation of APIs, etc.  Our aim
is to mention ideas that are at least somewhat beyond conventional best
practices. The ideas listed here have the potential to become best practices in
the medium to long-term. The ideas are presented roughly in the order of
increasing novelty.

@@

Except for \citet{ThielEtAl2020}, the research software guidelines that we
consulted do not mention linters.  However, we believe that linters have the potential
to improve code quality at a relatively low cost.  A linter is a tool that
statically analyzes code to find programming errors, stylistic inconsistencies
and suspicious constructs \citep{Wikipedia2022_Lint}. Linters can be used to
spot check code files, or even better as part of a continuous integration
system, as discussed in Section~\ref{Sec_CompareTools}.

@@

To address the pain point of a lack of funding (\ppref{P_LackFunding}), LBM
developers should watch for new opportunities to publish their research software
source code. For instance, the Journal of Open Source Software (JOSS) reviews
and publishes articles that credit the scholarship contained in the software
itself \citep{SmithEtAl2018-joss}.  \citet{SmithEtAl2016-softcite} presents a
set of software citation principles that may encourage broad adoption of a
consistent policy for software citation across disciplines and venues.
\citet{ChueHongEtAl2019} provides a software citation checklist for developers
to make a release of their software citable.  Further guidance on software
citation is provided by \citet{KatzEtAl2021}.  Another option is to use GitHub
for citation, since it is relatively easy to add metadata to repositories and to
generate citations for those repositories \citet{Smith2021-CitationsOnGitHub}.
